---
title: "Developing Data Products - Week 2 assignment"
author: "Mohammed Asif"
date: "16/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Assignment Objective
Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 


## Todays Date

```{r}
Sys.Date()
```

## Assignment submission Date

```{r}
as.Date("2021-03-16")
```

## Map of top 10 deaths in Indian States due to COVID - 30 Jan 2020 to 6 Aug 2020
Got the data from COVID-19 Corona Virus India Dataset here <https://www.kaggle.com/imdevskp/covid19-corona-virus-india-dataset?select=complete.csv>

### Load libraries
```{r}
library(dplyr)
library(leaflet)
library(htmltools)
```

### Get Data
```{r}
lin <- 'https://raw.githubusercontent.com/imdevskp/covid-19-india-data/master/complete.csv'
df <- read.csv(url(lin))
df$StateUT <- df$Name.of.State...UT
df$Death <- as.numeric(df$Death)
sorted <- df %>% group_by(StateUT, Latitude, Longitude) %>% summarise(Death = max(Death), .groups = 'drop')
arranged <- sorted %>% arrange(desc(Death)) %>% top_n(10)
```

### Show map

```{r}
map <- arranged %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup=paste
             ("<br>State/UT: ", 
               htmlEscape(arranged$StateUT), 
              "<br>Deaths: ", 
               htmlEscape(arranged$Death)
              ) 
            )
map
```